---
title: "p8105_hw2_sl5010"
author: "Fiona Li"
date: "10/2/2021"
output: github_document
---

## Problem 1

```{r}
library(tidyverse)
library(readxl)
```

### Read and clean the Mr. Trash Wheel sheet:

```{r}
TrasWheel_df = read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",range = "A2:N408")
TrasWheel_df = janitor::clean_names(TrasWheel_df)
names(TrasWheel_df)
TrasWheel_df = filter(TrasWheel_df, !is.na(dumpster))%>%
mutate(sports_balls = round(sports_balls))
TrasWheel_df

```

### Read and clean precipitation data for 2018 and 2019

```{r}
TrasWheel_df_18 = 
  read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2018 Precipitation", range = "A2:B14")%>%
  filter(!is.na(Total))%>%
  mutate(year = 2018)

TrasWheel_df_19= 
  read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",sheet = "2019 Precipitation", range = "A2:B14")%>%
  filter(!is.na(Total))%>%
  mutate(year = 2019)

TrasWheel_df_1819 = full_join(TrasWheel_df_18, TrasWheel_df_19)%>%
  mutate(Month = month.name[Month])

TrasWheel_df_1819
```
### Write a paragraph about these data
```{r}
skimr::skim(TrasWheel_df)
skimr::skim(TrasWheel_df_1819)
median =
  filter(TrasWheel_df, year == 2019)%>%
  pull(sports_balls)%>%
  median()
median

```

the number of observations in TrasWheel_df dataset is 344, and that in TrasWheel_df_1819 is 18. Key variables of TrasWheel_df is sports_balls, and key variables of TrasWheel_df_1819 is Total. For available data, the total precipitation in 2018 is 70.33, and the median number of sports balls in a dumpster in 2019 is 8.5.


