---
title: "p8105_hw2_sl5010"
author: "Fiona Li"
date: "10/2/2021"
output: github_document
---

## Problem 1

```{r}
library(tidyverse)
library(readxl)
```

### Read and clean the Mr. Trash Wheel sheet:

```{r}
TrasWheel_df = read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",range = "A2:N408")

TrasWheel_df = janitor::clean_names(TrasWheel_df)

names(TrasWheel_df)

TrasWheel_df = filter(TrasWheel_df, !is.na(dumpster)) %>%
mutate(sports_balls = round(sports_balls))
TrasWheel_df

```

### Read and clean precipitation data for 2018 and 2019

```{r}
TrasWheel_df_18 = 
  read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
             sheet = "2018 Precipitation", range = "A2:B14") %>%
  filter(!is.na(Total)) %>%
  mutate(year = 2018)

TrasWheel_df_19= 
  read_excel("Data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2019 Precipitation", range = "A2:B14") %>%
  filter(!is.na(Total)) %>%
  mutate(year = 2019)

TrasWheel_df_1819 = full_join(TrasWheel_df_18, TrasWheel_df_19) %>%
  mutate(Month = month.name[Month])

TrasWheel_df_1819
```
### Write a paragraph about these data
```{r}
skimr::skim(TrasWheel_df)
skimr::skim(TrasWheel_df_1819)
median =
  filter(TrasWheel_df, year == 2019)%>%
  pull(sports_balls)%>%
  median()
median

```

the number of observations in TrasWheel_df dataset is 344, and that in TrasWheel_df_1819 is 18. Key variables of TrasWheel_df is sports_balls, and key variables of TrasWheel_df_1819 is Total. For available data, the total precipitation in 2018 is 70.33, and the median number of sports balls in a dumpster in 2019 is 8.5.

## Problem 2

### clean the data in pols-month.csv.

```{r}
pols_month_df = 
  read.csv(file = "./data/pols-month.csv") %>%
  separate(mon, into = c("year", "month", "day"), sep ="-") %>%
  mutate(month = as.numeric(month)) %>%
  mutate(month = month.name[month]) %>%
  select(-day, -prez_gop, -prez_dem) %>%
  pivot_longer(
    gov_gop:rep_dem,
    names_to = "prez", 
    values_to = "president") %>%
  mutate(year = as.numeric(year))
pols_month_df
```
### Second, clean the data in snp.csv using a similar process to the above.

```{r}
snp_df = 
  read.csv(file = "./data/snp.csv") %>%
  separate(date, into = c("month", "day", "year"), sep ="/")%>%
  mutate(month = as.numeric(month)) %>%
  mutate(month = month.name[month]) %>%
  select(-day) %>%
  mutate(year = as.numeric(year))
  for (i in 1: nrow(snp_df)){
    if (snp_df$year[i] > 15) {snp_df$year[i] = snp_df$year[i]+1900}
    else {snp_df$year[i] = snp_df$year[i]+2000}
  }
snp_df = arrange(snp_df, year)
  
snp_df  
```
### Third, tidy the unemployment data so that it can be merged with the previous datasets.

```{r}
unemployment_df = 
  read.csv(file = "./data/unemployment.csv")%>%
  pivot_longer(
    Jan:Dec,
    names_to = "month", 
    values_to = "unemployment") %>%
  mutate(Year = as.double(Year)) %>%
  rename(year = Year)
 unemployment_df$month = match(unemployment_df$month,month.abb)
  unemployment_df$month = month.name[unemployment_df$month]

unemployment_df
```
### Join the datasets by merging snp into pols, and merging unemployment into the result.
```{r}
final_data = 
   left_join(pols_month_df,snp_df, by = c("month","year")) %>%
   left_join(unemployment_df, by = c("month","year"))
final_data
```

### Write a short paragraph about these datasets.

```{r}
dim(pols_month_df)
range(pull(pols_month_df,year))
names(pols_month_df)
dim(snp_df)
range(pull(snp_df,year))
names(snp_df)
dim(unemployment_df)
range(pull(unemployment_df,year))
names(unemployment_df)
dim(final_data)
range(pull(final_data,year))
names(final_data)
```

For pols_month_df, the dimension is (4932,4), range of years is (1947,2015), and names of key variables are "prez" and "president".

For snp_df, the dimension is (787,3), range of years is (1950,2015), and name of key variable is ""close".

For unemployment_df, the dimension is (816,3), range of years is (1948,2015), and name of key variable is "unemployment".

For final_data, the dimension is (4932,6), range of years is (1947,2015), and name of key variable is "prez", "president", "close", "unemployment".

## Problem 3

```{r}

```


